Manuscript

### 2017-07-25 manuscript.Rmd
Standardized variable names according to Boston dataset and removed the Northeasternmost census tract from the Denver dataset.

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
denver_tracts$Phys_Act <- denver_tracts$PhysAct
denver_tracts$CollegeDeg <- denver_tracts$CollegePercent
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

>>>>

# Methods
```{r load_data}
# I've standardized the variable names based on the Boston dataset, so let's use those variable names moving forward. I also removed the Northeasternmost census tract from the Denver dataset as you suggested.

denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
denver_tracts$Phys_Act <- denver_tracts$PhysAct
denver_tracts$CollegeDeg <- denver_tracts$CollegePercent
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")
